Interacting Classical Gas

### 2016-10-07 Interacting Classical Gas_Zhiyu_APS.tex
Oct7 APS's PRE format, tex

\documentclass[aps,pre,twocolumn
,groupedaddress]{revtex4-1}
%\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{bm}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \affiliation{Fudan University}
\begin{abstract}
\end{abstract}
 \maketitle
% \tableofcontents
% \newpage
\section{Introduction}

@@

>>>>

\documentclass[aps,pre,twocolumn
,groupedaddress]{revtex4-1}
%\documentclass[a4paper,onecolumn,12pt]{article}
\usepackage{amsmath}
 \usepackage{amsfonts}
 \usepackage{amssymb}
 \usepackage{graphicx}
 \usepackage{subfigure}
 \usepackage{enumerate}
 \usepackage{verbatim}% for \begin{comment} \end{comment}
 \usepackage{color}
 \usepackage{bm}
 \begin{document}
 \title{Interacting Classical Gas}
 \author{Zhiyu}
 \affiliation{Fudan University, Shanghai, China}

\begin{abstract}
\end{abstract}
 \maketitle
% \tableofcontents
% \newpage
\section{Introduction}

@@

One will say that this condition only means that the energy transfer in every collision is much smaller than the energy interval. It seems that these two regime are not so distinct. It is necessary to emphasis that the essential difference between these two regime lies in whether the energy transfer in every collision is correlated: In thermalizable regime, the energy transfer in every collision is much smaller than the energy interval, which definitly slows down the energy transfer. What is more, because of this, the particles is less interfered by other particles so that two-particle analysis survives. It means that for a particle pair, the energy transferred in this collision is correlated with the one in the next time! In this manner, each particle in the pair will pick up some energy in several collisions, and then return it back to its partner -- which is just what the long term beat effect tells us. Thus the particles energy is localized in certain value. On the contrary, if we go to non-thermalizable regime, the energy transfer is so fast that for each particle don't remember their partners. As a result, the energy transferred in every collision between two particles are no longer correlated, which is equivalent to say that two-particle analysis breaks down. Instead, the energy transfer is completely random, with a non-zero amplitude. On the single-particle energy diagram, what we expected to see is a ``one dimensional random walk" ,so energy levels quickly spread around the diagram.

To sum up, the thermalization threshold not only tells us whether the amplitude of energy transfer in every collision is small enough compared to particles' energy, but also shows whether the ``correlation time" of particle pair is much longer than the characteristic time of the system (the oscillation period).
